---
title: "Adding attr to columns of a DF"
output: html_document
---

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results='show', 
  tidy = FALSE,
  fig.path = 'figure_study/'
)

echoChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./scripts/issues/attributes_df_columns.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

I've recently imported an SPSS file to [one of the projects](https://github.com/IALSA/LASA), using a call
```
 Hmisc::spss.get(filePath, use.value.labels = TRUE)
```
The dataframe that came out of it had the following structure:
```{r load_demo, echo=echoChunks}
```
which was quite convenient, because I could have written a custom function to pair names of the variables and their descriptive labels into a separate dataset and print it for examination.

```{r nl_function, echo=echoChunks}
```

I would like to recreate this documentation structure from scratch. So I've taken the dataframe I'd like to annotate

```{r load_zero, echo=echoChunks}
```

and started changing the attributes in the following fashion:

```{r add_attributes, echo=echoChunks}
```

which was working out fine
```{r print_attributes, echo=echoChunks}
```

until I ran into <code>dplyr</code> problem:
```{r basic_counts, echo=echoChunks, eval=FALSE}
```

```
Quitting from lines 57-57 (attributes_df_columns.Rmd) 
Error in eval(expr, envir, enclos) : 
  column 'id' of type integer has unsupported attributes: label
Calls: <Anonymous> ... group_by_.data.frame -> grouped_df -> grouped_df_impl -> .Call

Execution halted
```

Should I try to mimic that attribute structure, which give gives me this flexibility?
```{r demo_counts, echo=echoChunks}
```
